\documentclass[a4paper,11pt]{article}

% ---------------------------------------------------------------
% Packages and Font Setup
% ---------------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage[margin=0.75in]{geometry}         % Set margins
\usepackage[T1]{fontenc}                     % Font encoding
% Original Helvetica settings removed:
% \usepackage[scaled]{helvet}                  % Helvetica font for modern look
% \renewcommand{\familydefault}{\sfdefault}    % Use sans-serif throughout
\usepackage{xcolor}                          % For colored text
\usepackage[colorlinks=true,linkcolor=primary,urlcolor=primary,citecolor=primary]{hyperref}             % Colored hyperlinks
\usepackage{enumitem}                        % Custom bullet lists
\usepackage{tabularx}                        % For tables
\usepackage{ragged2e}                        % For text alignment
\usepackage{setspace}                        % Adjust line spacing
\usepackage{titlesec}                        % For section formatting
\usepackage{iftex}                           % Check if engine is pdflatex, xetex or luatex

% Font settings from ABC LaTeX code
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

% ---------------------------------------------------------------
% Colors
% ---------------------------------------------------------------
\definecolor{primary}{RGB}{0,82,113}
\definecolor{accent}{RGB}{0,110,142}
\definecolor{lightgray}{RGB}{245,245,245}
\definecolor{darkgray}{RGB}{70,70,70}

% ---------------------------------------------------------------
% Custom Section Title Formatting
% ---------------------------------------------------------------
\titleformat{\section}{\Large\bfseries\scshape\raggedright\color{primary}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{10pt}

% ---------------------------------------------------------------
% General Formatting Settings
% ---------------------------------------------------------------
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=5pt, parsep=2pt}
\renewcommand{\baselinestretch}{1.05}

% ---------------------------------------------------------------
% Header Command with Icons (ATS-friendly: icons are for visual appeal only)
% ---------------------------------------------------------------
\newcommand{\header}[4]{
{\centering{\Huge\textbf{#1}}\par}
\vspace{4pt}
\centering{
    Phone: \href{tel:#2}{#2} \quad $|$ \quad
    Email: \href{mailto:#3}{#3} \quad $|$ \quad
    LinkedIn: \href{#4}{AbdulSheikh}
}
\vspace{-6pt}
}

% ---------------------------------------------------------------
% Section Title Command
% ---------------------------------------------------------------
\newcommand{\sectiontitle}[1]{\section*{#1}}

% ---------------------------------------------------------------
% Experience Entry Command (for concise listing)
% ---------------------------------------------------------------
\newcommand{\experienceentry}[4]{
\textbf{\textcolor{primary}{#1}} \hfill \textbf{#2} \\
\textit{#3} \hfill \textit{#4} \\
}

% ---------------------------------------------------------------
% Project Entry Command
% ---------------------------------------------------------------
\newcommand{\projectentry}[2]{
\raggedright\textbf{\textcolor{primary}{#1}}: \textit{#2} \\
}

% ---------------------------------------------------------------
% Begin Document
% ---------------------------------------------------------------
\begin{document}

% ---------------------------------------------------------------
% 1. CONTACT INFORMATION & PROFESSIONAL LINKS
% ---------------------------------------------------------------
\header{Abdul Sheikh}{+91 8999849906}{abdulsheikh9279@gmail.com}{https://www.linkedin.com/in/abdul-sheikh-727b60246/}

% ---------------------------------------------------------------
% 2. PROFESSIONAL SUMMARY
% ---------------------------------------------------------------
\sectiontitle{Professional Summary}
\begin{itemize}
\item \textbf{Computer Science (Artificial Intelligence)} student with strong foundations in \textbf{software development and computer vision systems}.
\item \textbf{Real-time AI applications} using TensorFlow Lite, OpenCV, and Raspberry Pi.
\item \textbf{End-to-end systems}, integrating hardware and software for real-world use cases.
\item \textbf{Core computer science concepts} including OOP, DBMS, and machine learning.
\item \textbf{Secure and reliable system design} through industry-focused internships and projects.
\end{itemize}

% ---------------------------------------------------------------
% 3. TECHNICAL SKILLS MATRIX
% ---------------------------------------------------------------
\sectiontitle{Technical Skills}
\begin{itemize}[leftmargin=*]
\item \textbf{Programming Languages/Core Concepts:} Java, Python, C, SQL, Object-Oriented Programming (OOP), Database Management Systems (DBMS), Machine Learning, Artificial Intelligence, Data Science
\item \textbf{Web \& Development Technologies:} HTML, CSS, JavaScript, React.js, Git, GitHub
\item \textbf{AI / ML \& Computer Vision:} TensorFlow Lite, YOLO, OpenCV, OCR (Tesseract)
\item \textbf{Data \& Analysis Libraries:} NumPy, Pandas, Matplotlib
\item \textbf{Platforms:} Raspberry Pi, Linux (Basic)
\end{itemize}

% ---------------------------------------------------------------
% 5. KEY PROJECTS
% ---------------------------------------------------------------
\sectiontitle{Key Projects}
\projectentry{Two-Wheeler Helmet Detection System}{Technologies: TensorFlow Lite, Raspberry Pi, OpenCV}
\begin{itemize}
\item Developed a real-time helmet detection system to improve rider safety.
\item Automated ignition lock mechanism based on helmet detection.
\item Achieved \textbf{85--90\% model accuracy} using a custom-trained TensorFlow Lite model.
\item Implemented a complete real-time pipeline on Raspberry Pi using OpenCV and servo motor control.
\end{itemize}

\projectentry{Smart Audio Description Glasses}{Technologies: Raspberry Pi, OpenCV, OCR}
\begin{itemize}
\item Built assistive smart glasses for visually impaired users using real-time OCR and object detection.
\item Integrated text-to-speech functionality, reducing information access time by approximately \textbf{70\%}.
\item Delivered a fully functional prototype using Raspberry Pi and OpenCV.
\end{itemize}

\projectentry{Tiger Detection \& Re-Identification System}{Technologies: YOLOv8, ResNet, ORB, Python}
\begin{itemize}
\item Designed an automated wildlife monitoring system using deep learning models.
\item Implemented ORB-based feature matching and centroid tracking for re-identification.
\item Improved recognition reliability by approximately \textbf{40\%} and built an incremental tiger profile database.
\end{itemize}

% ---------------------------------------------------------------
% 6. CERTIFICATIONS
% ---------------------------------------------------------------
\sectiontitle{Certifications}
\begin{tabularx}{\textwidth}{X r}
\textbf{Data Analytics Job Simulation} - Deloitte & September 2025 \\
\textbf{Software Engineering Job Simulation} - Forage & September 2025 \\
\textbf{Bring AI to Work Workshop} - Google Workspace Admins & June 2025 \\
\textbf{Introduction to Prompt Engineering} - Simplilearn & April 2025 \\
\textbf{Introduction to Generative AI Art of the Possible} - Amazon Web Services (AWS) & August 2024 \\
\end{tabularx}

% ---------------------------------------------------------------
% 7. EDUCATION
% ---------------------------------------------------------------
\sectiontitle{Education}
\begin{tabularx}{\textwidth}{X r}

\textbf{Btech (Computer Science and Engineering (AI))} 
& August 2023 -- August 2027 \\
Vishwakarma Institute of Technology (VIT), Pune, Maharashtra 
& CGPA: 8.27/10 \\[8pt]

\textbf{Higher Secondary Certificate (HSC)} 
& August 2021 -- August 2022 \\
Shri Shivaji Junior College, Chandrapur, Maharashtra 
& Percentage: 84.83\% \\[8pt]

\textbf{Secondary School Certificate (SSC)} 
& August 2019 -- August 2020 \\
Shri Shivaji Junior College, Chandrapur, Maharashtra 
& Percentage: 90.40\% \\

\end{tabularx}

% ---------------------------------------------------------------
% LEADERSHIP & RESPONSIBILITY
% ---------------------------------------------------------------
\section{Leadership \& Responsibility}

\textbf{Multimedia Incharge -- Eklavya Club, VIT Pune}
\begin{itemize}[leftmargin=*]
    \item Managed design and social media content for major college events.
    \item Created posters and promotional material to improve student engagement.
    \item Handled end-to-end online promotions with timely delivery.
\end{itemize}

% ---------------------------------------------------------------
% 8. LANGUAGES
% ---------------------------------------------------------------
\sectiontitle{Languages}
\begin{tabularx}{\textwidth}{X r}
\textbf{English} & Full Professional Proficiency \\
\textbf{Hindi} & Native or Bilingual Proficiency \\
\textbf{Marathi} & Native or Bilingual Proficiency \\
\end{tabularx}

% ---------------------------------------------------------------
% NOTES: FORMATTING & ATS OPTIMIZATION
% ---------------------------------------------------------------
% - Reformatted to use the Latin Modern font instead of Helvetica.
% - Robust bullet points with dynamic action verbs and quantifiable metrics enhance recruiter appeal.
% - Standard section headings and clear tool names ensure ATS compatibility.
\end{document}

